% !TeX root = ../FinalRepordCS.tex

\chapter{Conclusion and Future Work}

\section{Conclusion}
In conclusion, this study has delved into the realm of Internet of Things (IoT) with a focus on data security, particularly in industrial settings. The significance of securing data in the vast and evolving IoT landscape cannot be overstated, especially as industries increasingly rely on interconnected devices and systems.

The study has specifically explored methods and algorithms for physical layer key generation in wireless communication, with a spotlight on the LoRa protocol. The implementation of LoRa nodes, a RSSI-based physical key generation, a Chacha20 encryption in LoRa nodes, and various signal processing techniques has been presented, along with real-world tests in both outdoor and indoor environments. The results indicate the feasibility and effectiveness of the proposed system, providing a foundation for secure communication in IoT applications.

\section{Future Work}

While this study has laid the groundwork for LoRa Physical Layer Key Generation, there are avenues for future research and development:

Scalability and Interoperability: Investigate the scalability of the proposed system to handle a larger number of devices and its interoperability with diverse IoT ecosystems.

Optimization and Efficiency: Explore ways to optimize the key generation process for improved efficiency, considering factors such as computational resources and energy consumption.

Security Analysis: Conduct a thorough security analysis to identify potential vulnerabilities and propose countermeasures to enhance the robustness of the system.


Real-world Deployment: Conduct extensive real-world deployment in various industrial settings to validate the system's performance and reliability in diverse environments.

 User-friendly Interfaces: Develop user-friendly interfaces and tools for easy configuration and management, making it accessible for a broader range of users.

Standardization Efforts: Contribute to standardization efforts in the field of IoT security, ensuring compatibility and adherence to industry standards.